### 2018-01-15 Atomic Spectra/paper.tex
added residuals plot

The relationship between the observed wavelength and the
scale reading on the spectrometer was calculated.
This was done by subtracting $\lambda_0$ from all of the values in the wavelength column of
\figHelium and then taking the reciprocals to get the values of the independent
variables.
All uncertainties were propagated using the method of quadratures.
The scale column formed the values for the dependent variable.
Applying the fit yielded a slope of $(2.00\pm.02)\x\SI{E-6}{\meter}$ and a
y-intercept of $(1.83\pm.09)$.
The $R^2$ value for the fit s 0.999489.
TODO ADD CHI SQUARED AND RESIDUALS\\

>>>>

The relationship between the observed wavelength and the
scale reading on the spectrometer was calculated.
This was done by subtracting $\lambda_0$ from all of the values in the wavelength column of
\figHelium and then taking the reciprocals to get the values of the independent
variables.
All uncertainties were propagated using the method of quadratures.
The scale column formed the values for the dependent variable.
Applying the fit yielded a slope of $(2.00\pm.02)\x\SI{E-6}{\meter}$ and a
y-intercept of $(1.83\pm.09)$.
The $R^2$ value for the fit s 0.999489.
The reduced $ \chi^2 $ obtained is $ 12.5827907379 $ with residuals visualized below.

\paperfig{Residuals}{\begin{tikzpicture}[scale = 0.95]
	\begin{axis}
		[width=\linewidth,
		tick label style={font=\fontsize{10pt}{1em}},
		xlabel={\fontsize{10pt}{1em}\selectfont $\lambda$ (\si{\nm}) $\rightarrow$},
		ylabel={\fontsize{10pt}{1em}\selectfont $ y - y_{fit} \rightarrow$},
		\paperaxis{Residuals vs. Wavelength}{y}{x}{450}{-0.15}{750}{0.15}{0}{2}]
		\papergraphoutline{450}{0}{750}{0};
		\addplot[color = black, only marks, mark = o, mark size = 1.5, error bars/.cd,
		y dir = both, y explicit, x dir = both, x explicit] 
		coordinates {
			(706.5, 0.0836354) (667.8, 0.00358039) (587.6, -0.13242233)
			(501.6, 0.01987709) (492.2, 0.01029522) (471.3, 0.00550431)
			(447.1, 0.00952993)
		};
	\end{axis}
\end{tikzpicture}}{WHAT TO ADD HERE?}
